Shapes analysis for time series

### 2024-10-25 NEURIPS24/paper.tex
change time seriesgraph

However, a graph time series transformation by a general diffeomorphism is not always a graph time series, see e.g. \Cref{fig:diffeo}, thus a graph time series is more than a simple curve \cite{glaunes2008large}. Our contributions arise from this observation: we specify the class of diffeomorphisms to consider and show how to learn them. This change is fruitful in representing transformations of time series graphs as illustrated in \Cref{fig:transport}.

>>>>

However, a time series graph transformation by a general diffeomorphism is not always a time series graph, see e.g. \Cref{fig:diffeo}, thus a time series graph is more than a simple curve \cite{glaunes2008large}. Our contributions arise from this observation: we specify the class of diffeomorphisms to consider and show how to learn them. This change is fruitful in representing transformations of time series graphs as illustrated in \Cref{fig:transport}.
